The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-06 analysis/paper/paper.qmd
Update package list

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                               # Managing paths
  "tidyverse", "reshape2", "widyr",     # Data manipulation and visualisation
  "furrr",                              # Parallel use of purrr::map() functions
  "tidytext", "SnowballC", "tm",        # Text processing and analysis
  "topicmodels", "LDAvis",              # Topic modeling
  "tidygeocoder",                       # Working with spatial data
  "igraph", "ggraph"                    # Network analysis and visualization
)

>>>>

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                       # Managing paths
  "tidyverse", "reshape2", "widyr", "readxl",  # Data manipulation and visualisation
  "furrr",                                      # Parallel use of purrr::map() functions
  "tidytext", "SnowballC", "tm",                # Text processing and analysis
  "topicmodels", "LDAvis",                      # Topic modeling
  "tidygeocoder",                               # Working with spatial data
  "igraph", "ggraph"                            # Network analysis and visualization
)
